Using high-resolution variant frequencies to empower clinical genome interpretation

### 2016-09-29 manuscript/manuscript.Rmd
Converting to GiM style

bibliography: "references.bib"
csl: "nature.csl"
---

@@

## Short running title: Using variant frequencies to empower genome interpretation

@@

Corespondance should be addressed to:
Dr James Ware, National Heart and Lung Institute, Imperial College London, London, Tel: Fax: Email: j.ware@imperial.ac.uk

@@

Key words:

@@

## Data availability

>>>>

bibliography: "references.bib"
csl: "american-medical-association.csl"
---

@@

**Short running title: Allele frequency and genome interpretation**

@@

Corespondance should be addressed to:
Dr James Ware, Cardiovascular Genetics and Genomics, NHLI, RBH Campus, Imperial College London, London, SW3 6NP; Tel: +44 20 7352 8121; Fax: +44 20 7351 8146; Email: j.ware@imperial.ac.uk

## CONFLICT OF INTEREST NOTIFICATION

The authors have no conflicts of interest to declare.

@@

Key words: Variant interpretation, Clinical Genomics, Allele frequency, Cardiomyopathy, Inherited Cardiovascular conditions, ExAC

@@

### Data availability
